---
title: Tidy Tuesday
author: Ingrid Zoll
date: '2021-03-18'
slug: tidy-tuesday-march-16
categories: []
tags: [RStudio, tidytuesday]
subtitle: ''
summary: ''
authors: []
lastmod: '2021-03-18T11:59:19-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE}
library(tidytuesdayR)
library(tidyverse)
library(lubridate)
library(ggdark)
library(wesanderson)
```

```{r loading data, message=FALSE, warning=FALSE, results='hide'}
# Get the Data
tuesdata <- tidytuesdayR::tt_load('2021-03-16')
games <- tuesdata$games
```

```{r by month popularity, message=FALSE, warning=FALSE}
mostpop_bymonth <- games %>%
  unite(yearmonth, month:year)%>%
  mutate(date = my(yearmonth)) %>%
  group_by(date)%>% 
  top_n(3, avg) %>% 
  ungroup %>%
  add_count(gamename, name = "count") %>%
  mutate(label = gamename, label = case_when(
    count < 10 ~ "Other games",
    count > 10 ~ gamename)) %>%
  mutate(game = factor(label), game = fct_infreq(label)) %>%
  mutate(game = str_replace(game, "PLAYERUNKNOWN'S BATTLEGROUNDS", "PUBG"), 
         game = str_replace(game, "Counter-Strike: Global Offensive", "CS GO"))
```

```{r, message=FALSE, warning=FALSE}
ggplot(mostpop_bymonth, aes(x=date, y=avg, fill=game))+
  geom_col(position="stack")+
  scale_fill_manual(values = wes_palette("Zissou1"))+
  dark_theme_gray()+
  labs(caption = "PUBG = PlayerUnknown's BattleGround \nCS GO = Counter-Strike: Global Offensive",
       title= "The Three Most Popular Games on Steam by Month", 
       y="Average number of players at the same time", x="Date")
```

```{r}
ggplot(mostpop_bymonth, aes(x=date, y=avg, fill=game))+
  geom_col(position="dodge")+
  scale_fill_manual(values = wes_palette("Zissou1"))+
  dark_theme_gray() +
  labs(caption = "PUBG = PlayerUnknown's BattleGround \nCS GO = Counter-Strike: Global Offensive",
       title= "The Three Most Popular Games on Steam by Month", 
       y="Average number of players at the same time", x="Date")
```

```{r, message=FALSE, warning=FALSE}
populargames <- mostpop_bymonth %>%
  filter(game == "CS GO" | game == "PUBG"| game == "Dota 2")
```

```{r}
ggplot(populargames, aes(x=date, y=avg))+
  dark_theme_gray()+
  scale_color_manual(name = 'Game', values =c('CS GO'="#F21A00",'Dota 2'="#EBCC2A", 'PUBG' = "#3B9AB2"),
        labels = c("CS GO", "Dota 2", "PUBG"))+
  geom_linerange(aes(ymax=peak, ymin=avg, color=game), size=.25)+
  geom_point(aes(y=peak, color=game), size=.7)+
  geom_point(aes(y=avg, color=game), size=.7)+
  labs(title="Three Most Popular Games", x="Date", y="Number of players")
```

```{r witcher 1, message=FALSE, warning=FALSE}
witcher <- games %>%
  filter(gamename == c("The Witcher 3: Wild Hunt")) %>%
  unite(yearmonth, month:year)%>%
  mutate(date = my(yearmonth))


release <- ymd("2019-12-20")
label <- ymd("2019-02-01")

ggplot(witcher, aes(x=date, y=avg))+
  theme(legend.position = "bottom")+
  scale_color_manual(name = 'Player Number \nMeasurement', values =c('gold'="#E1AF00",'skyblue3'="#78B7C5"), labels = c("Peak", "Average"))+
  dark_theme_gray()+
  geom_vline(aes(xintercept = release), color="grey95", linetype="dashed")+
  labs(x="Date", y="Number of players at the same time")+
  annotate(geom = "text", x = label, y = 75000, 
  label = "Dec 20, 2019: Release of \n \"The Witcher\" TV show", color="grey94", size=3)+
  geom_point(aes(y=peak, color="gold"))+
  geom_line(aes(color="skyblue3"))+
  labs(title="The Witcher 3: Wild Hunt", subtitle= "Average and peak player numbers per month")
```

Initially when I looked at this graph, I noticed a few things: first, the massive spike in activity in late 2019/early 2020, and the smaller (but still notable) spike in the summer of 2016. The larger spike can be attributed to the release of The Witcher TV show on netflix, but the smaller peak took me longer to figure out. Steam has an annual summer sale, and by best guess is that the game went on sale in the summer of 2016, so many new players bought it and started to play. 

```{r, message=FALSE, warning=FALSE}
ggplot(witcher, aes(x=date, y=gain))+
  theme(legend.position = "bottom")+
  dark_theme_gray()+
  geom_vline(aes(xintercept = release), color="grey95", linetype="dashed")+
  labs(x="Date", y="Number of players at the same time")+
  annotate(geom = "text", x = label, y = 25000, 
  label = "Dec 20, 2019: Release of \n \"The Witcher\" TV show", color="grey94", size=3)+
  geom_line(aes(y=avg), color="#EBCC2A")+
  geom_col(aes(fill="gains"), fill="#3B9AB2")+
  labs(title="The Witcher 3: Wild Hunt", subtitle="Average number of players at the same time with montly gains or losses")
```

Lastly, I wanted to look at the gains (and losses) of player activity. There's nothing too interesting in this graph, but I thought it added another cool visualization to this post. 
