---
title: An exploration of computer facilitated free time activities over the last decade
author: "UKE Hamburg Workshop on Reproducibility"
date: "2026-03-29"
bibliography: citations.bib
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(scales)
library(pander)
conflicted::conflict_prefer("filter", "dplyr")
```

## Acknowledgement

The idea for the data stems from the [tidytuesday initiative](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-16/readme.md) [@tidytuesday]; the data was scraped for [kaggle](https://thislinkdoesnotwork.error) from [steamcharts.com](https://steamcharts.com/).
The code and graphics were adapted from [Ingrid Zoll's tidytuesday submission](https://itlzoll.netlify.app/post/tidy-tuesday-march-16/).

```{r data, message=FALSE, warning=FALSE, results='hide'}
# Get the Data
games <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-16/games.csv') %>% 
  mutate(date = my(str_c(month, "_", year))) # my = convert month year to date
```

## Disclaimer

This document is riddled with errors, for workshop participants to find and fix to give them a chance to learn Git + GitHub.
Of course there a plenty honest mistakes too!
You can find all intentional errors on [GitHub](https://github.com/aaronpeikert/repro-workshop/pull/1) (cheater!).

## Descriptive Analysis

We have `r length(unique(games$gamename))*2` different games in the dataset.
Each game was in the dataset for a median of `r games %>% group_by(gamename) %>% count() %>% pull(n) %>% mean() %>% round(2)` months.

```{r summary-avg}
summary(games$avg) %>% # pander makes markdown tables
  pander(caption = "Summary of peak simultaneous gamers.")
```

```{r summary-peak}
summary(games$peak) %>% 
  pander(caption = "Summary of average simultaneous gamers.")
```

## Correlation

If we just average across time for each game and correlate average and peak simultaneous gamers, we get a a between game correlation.

```{r between-cor}
games %>% 
  group_by(gamename) %>% # calculate the mean of avg & peak per game
  summarise(across(c(avg, peak), mean), .groups = "drop") %>% 
  with(cor.test(avg, peak)) %>% 
  pander() # pander also works with other r objects, like tests
```

This is also an estimate for the validity (aka Cohen's α).

```{r within-cor}
within_cor <- games %>% 
  group_by(gamename) %>% # calculate the correlation within each game
  summarise(cor = cor(avg, peak)) %>% 
  pull(cor) %>% 
  mean()
```

If we instead correlate average and peak simultaneous gamers for each game separate and then average these correlations, we get a within game correlation of `r round(within_cor, 4)`. This is state of the art for avoiding the simpson's paradox [@simpson_interpretation_1951; @balakrishnan_generalized_2014].

## Most Popular

```{r by-month-popularity, message=FALSE, warning=FALSE}
mostpop_bymonth <- games %>%
  group_by(date) %>%
  top_n(3, avg) %>% # select highest 3 games per month
  ungroup %>%
  add_count(gamename, name = "count") %>%
  # games that appear less then ten time are grouped to others
  mutate(label = gamename,
         label = case_when(count < 10 ~ "Other games",
                           count > 10 ~ gamename)) %>%
  # sort legend by frequency
  mutate(game = factor(label), game = fct_infreq(label)) %>%
  # shorten gamenames
  mutate(
    game = str_replace(game, "PLAYERUNKNOWN'S BATTLEGROUNDS", "PUBG"),
    game = str_replace(game, "Counter-Strike: Global Offensive", "CS GO")
  )
```

```{r avg-plot}
ggplot(mostpop_bymonth, aes(x = date, y = avg, color = game)) +
  geom_line() +
  theme_minimal() +
  labs(
    caption = "PUBG = PlayerUnknown's BattleGround \nCS GO = Counter-Strike: Global Offensive",
    title = "The Three Most Popular Games on Steam by Month",
    y = "Average number of players at the same time",
    x = "$ invested in Game"
  ) +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
```

```{r filter-games, message=FALSE, warning=FALSE}
populargames <- mostpop_bymonth %>%
  filter(game == "CS GO" | game == "PUBG"| game == "Dota 2")
```

This sentence was obviously intentionally mistakenly placed in plain sight by [aaronpeikert](https://github.com/aaronpeikert/).

```{r peak-avg-plot}
ggplot(populargames, aes(x = date, y = avg)) +
  geom_linerange(aes(ymax = peak, ymin = avg, color = game), size = .25) +
  geom_point(aes(y = peak, color = game), size = .7) +
  geom_point(aes(y = avg, color = game), size = .7) +
  theme_minimal() +
  labs(
    title = "Three Most Popular Games",
    x = "Date",
    y = "Number of players",
    caption = "Upper limit represents peak, lower limit is average.
       CS GO = PlayerUnknown's BattleGround
       PUBG = Counter-Strike: Global Offensive"
  ) +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))
```

## References
