---
title: "Reproducible Research in R"
subtitle: "How to do the same thing more than once"
author: 
  - "Aaron Peikert"
date: 'Marbach Castle | `r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---
class: inverse, center, middle

# Why should we work reproducibly?

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=4, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE,
  dev = "svglite"
)
library("tidyverse")
library("patchwork")
library("xaringanthemer")
library("svglite")
library("qrcode")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
primary_color <- "#024959"
secondary_color <- "#F28705"
style_duo(
  primary_color = primary_color,
  secondary_color = secondary_color,
  header_font_google = google_font("Didact Gothic", "400", "400i"),
  text_font_google   = google_font("IBM Plex Sans", "400", "400i"),
  text_font_size = "1.5rem",
  )

style_extra_css(css = list(".todo" = list(color = "#17C25B"),
                           ".optional" = list(color = "#05BCE6"),
                           ".large" = list(`font-size` = "130%")),
                )
```

---
class: inverse, center, middle

# ~~Why~~ How should we work reproducibly?

---

## How to behave in this workshop?

1. Be nice and help each other.
2. Don't be shy: Answer and ask questions, even stupid ones.
3. .todo[Do things in this color.]
4. .optional[Try things in this color (they are completely optional).]

--

## Let's try it.

---

## Slides

```{r, echo=FALSE}
link <- "https://github.com/aaronpeikert"
```

```{r, echo=FALSE, out.width = "30%", out.extra='style="float:right; padding:10px"'}
generate_svg(qr_code(link), here::here("images/", "qr_slides.svg"), foreground = secondary_color, background = primary_color, show = FALSE)
knitr::include_graphics("images/qr_slides.svg")
```

.todo[Tell your neighbors your name and how familiar you are with R.]

--

Which color means: "this task is optional"?

--

Do you have a question?

--

.todo[Open this link to get the materials:]

`r link`

--

.optional[Scan the QR code (→) to get the materials:]

???

1. Be nice and help each other.
2. Don't be shy: Answer and ask questions, even stupid once.
3. .todo[Do things in this color.]
4. .optional[Try things in this color (they are completely optional).]

Workshop within the workshop.

---
class: inverse, center, middle

# Goals

---
class: middle

.center[

.large[code + data]

```{r, echo=FALSE, out.width='30%'}
knitr::include_graphics("https://publicdomainvectors.org/download.php?file=CARTON01.svg")
```

]

---

## The Boring Stuff

.pull-left[

```{r, child="snippets/signin.Rmd"}
```

]

.pull-left[

```{r, child="snippets/signup.Rmd"}
```

]

---

# A single script

.todo[Look around, become comfortable. Then, locate the files pane.]

--

.todo[Open the R folder.]

.todo[Click on the file `R/prepare_games.R`]

.optional[Take a look at `R/prepare_inflation.R` (same thing but more complicated)]

---

# An incomplete list of best practices

1. list requirements early
2. use relative locations
3. document relevant information

---

# A few principles of documentation


.center[
document relevant information = lot of writing

?]

--

## No
--
, not necessarily.

--

1. What is *standard* does not have to be documented.
2. What is *easy* needs only little documentation.
3. What is *consistent* only has to be documented once.

---
class: inverse, center, middle

# Goals

---
class: middle

.center[

.large[code + data + text + software + history + workflow]

```{r, echo=FALSE, out.width='30%'}
knitr::include_graphics("https://publicdomainvectors.org/download.php?file=CARTON01.svg")
```

]

---
## Goals for today

Ultimate reproducibility for a toy(-ish) project:

1. Fully open: data, code, software
2. Fully automated: from raw data (csv, excel) to paper (html, pdf)
2. Across machines
2. Across time

And provide tangible proof for 1-3 via automated public reproduction in the cloud/GitHub Actions.

---

## Not goals for today (though possible)

1. beyond R (but works the same for Python/Julia/Octave)
2. data > 100MB, analysis > 1h / 1 CPU
3. complicated tables / formatting / die hard word lovers

---
background-color: #F0F8F8


.center[

```{r, echo=FALSE, out.width='90%'}
knitr::include_graphics("https://raw.githubusercontent.com/aaronpeikert/repro-tutorial/main/images/nutshell.svg")
```

]

