---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Ensuring Reproducibility of complex data analytic projects

<!-- badges: start -->
<!-- badges: end -->

Can I trust these results \[to reproduce\]?
In this workshop (2 x 4h) participants learn to spot threats to reproducibility and develop the skills to avoid them.
These skills stem from hard learned lessons of the software engineering community, which developed tools the research community can utilize.
The employed tools, namely RMarkdown, Git, Make, and Docker, do not merely increase the shelf life of an analysis, they help researchers to be more productive and collaborate easier.
Researchers who routinely use R will benefit most, however all presented principles (and most tools) work well with other programming languages.

# Requirements

```{r, child="requirements.Rmd"}
```

# Roadmap

```{r, child="plan.Rmd"}
```
