---
title: "Summary"
author: "Aaron Peikert"
date: "3/30/2021"
bibliography: citations.bib
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(cowplot)
library(magick)
```

## Bird's-eye view

```{r}
plot(ggdraw() + draw_image("https://raw.githubusercontent.com/aaronpeikert/repro-thesis/master/images/idealized-workflow.svg"))
```

## Install Software on Windows

Press Windows key + X, click on "Windows Powershell (Admin)". Paste:

```
Set-ExecutionPolicy Bypass -Scope Process -Force;
[System.Net.ServicePointManager]::SecurityProtocol =
[System.Net.ServicePointManager]::SecurityProtocol -bor 3072;
iex ((New-Object System.Net.WebClient).
DownloadString('https://chocolatey.org/install.ps1'))
```

Close and reopen Powershell:

```
choco install -y r r.studio rtools git make docker
```

Open RStudio:

```{r, eval=FALSE, echo=TRUE}
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/repro")
```

## New Project

RStudio → File → New Project → New Directory → New Project

Add README.Rmd, a license and a Code of Conduct:

```{r, eval=FALSE, echo=TRUE}
library(usethis)
use_readme_rmd()
use_cc0_license()
use_code_of_conduct()
```

## RMarkdown

Take a look at `summary.Rmd` and `games.Rmd`.

````
Text and **cool** code [@tidytuesday].

```r
t.test(extra ~ group, data = sleep)
```
````

Text and **cool** code [@tidytuesday].

```{r, echo=TRUE}
t.test(extra ~ group, data = sleep)
```

## Set Up Git

```{r, eval=FALSE, echo=TRUE}
usethis::use_git_config(user.name = "Jane Doe", user.email = "jane@example.org")
```

```{r, eval=FALSE, echo=TRUE}
usethis::create_github_token() # copy token
gitcreds::gitcreds_set() # overwrite when necesary, paste token
```

## No Git

```{r}
no_git <- image_quantize(image_read("https://happygitwithr.com/img/no_github.png"), colorspace = 'gray')
plot(ggdraw() + draw_image(no_git))
```

## Some Git

```{r, eval=FALSE, echo=TRUE}
use_git() # everthing is local
```

```{r}
plot(ggdraw() + draw_image("https://happygitwithr.com/img/no_github.png"))
```

## Some GitHub

```{r, eval=FALSE, echo=TRUE}
use_github() # stuff is uploaded, you may want `private = TRUE`
```

```{r}
plot(ggdraw() + draw_image("https://happygitwithr.com/img/ours-you.png"))
```

## No write access

```{r, eval=FALSE, echo=TRUE}
create_from_github("aaronpeikert/repro-workshop", fork = FALSE)
```

```{r}
plot(ggdraw() + draw_image("https://happygitwithr.com/img/theirs.png"))
```

## Fork

```{r, eval=FALSE, echo=TRUE}
create_from_github("aaronpeikert/repro-workshop", fork = TRUE)
```

```{r}
plot(ggdraw() + draw_image("https://happygitwithr.com/img/fork-them.png"))
```

## Write access

```{r, eval=FALSE, echo=TRUE}
create_from_github("teammember/repro-workshop")
```

```{r}
plot(ggdraw() + draw_image("https://happygitwithr.com/img/ours-them.png"))
```

## Git Check

```
git remote get-url origin
```

## Git Reset

```
git fetch origin
git reset --hard origin/master
```

## games.Rmd teamlead

Only teamlead!!!

Copy games.Rmd from

https://raw.githubusercontent.com/aaronpeikert/repro-workshop/master/games.Rmd

Commit

Push

## games.Rmd team

Pull

## Issues to coordinate


Each one, open an issue.

Don't do anything else. Wait.

```
usethis::browse_github_issues()
```

## Assign Issue

assign one of the other issue to yourself

Remember issue number i.g. #4

wait.

## Create Branch/Inititate PR

Change to your remembered issue number:

```{r eval=FALSE, echo=TRUE}
usethis::pr_init("fix-issuenumber")
```

Make changes.

Commit. Don't Push!

Wait.

## Create PR

```{r, eval=FALSE, echo=TRUE}
usethis::pr_push()
```

Request a reviewer.

## References
