# Version Control {-}

```{r results='asis', echo = FALSE}
reprodude2 <- generate_reprodudes(links$reprodudes$three,
                                  "ReproDude",
                                  "Hey, I'm your ReproDude for this chapter. If you have any questions click on me and we can talk!")

cat(reprodude2)

```

## What now? {-}

Let's get on with it then! 
What's next?

let's take another look at our components, which ones are we examining now?

code + data + text + <span style="color:orange">history</span> + software + workflow

History? Maybe a look at our problem and software solution list will help to shed some light on the matter.

Problem list:

1. ~~copy&paste mistakes~~
2. <span style="color:orange">inconsistent versions of code or data</span>
3. missing or incompatible software
4. complicated or ambiguous procedure for reproduction

Software solution list:

1. RMarkdown
2. <span style="color:orange">Git</span>
3. Docker
4. Make

So that means we use the Git (and Github) to avoid the problem of inconsistent versions of code and data?

That sounds good, let's get started right away!

## Git {-}

```{r, echo=FALSE, fig.cap="My SVG Picture"}
knitr::include_graphics("Git Diagram.svg")
```

Git is an amazing tool that helps you keep track of changes in your project, just like having a magical time machine for your work. 
It's like having a superpower for managing files and projects, especially when you're coding, although it can be used for any type of project that involves files.

Imagine you have a project, and it's like a journey represented by a single line called the 'main' branch.
Each point along this line is a different version of your project, capturing the moments when you've made changes and saved them (committed them). 
It's like preserving snapshots of your progress, allowing you to travel back in time and see how your project evolved.

### Hands on {-}

Now that we've cleared that up, let's get back to the code.

<span style="color:orange">Modify this code and run it:</span>

```
# use a function without loading the package
# package::function
usethis::use_git_config(
  user.name = "Jane Doe", # <-- change to your name
  user.email = "jane@example.org", # <-- and your email
  init.defaultBranch = "main") # <-- not necessary but kinder than 'master'
```
You will need to do this *once for each computing environment*.

Let us now activate Git.

```
# use a function without loading the package
# package::function
usethis::use_git_config(
  user.name = "Jane Doe",
  user.email = "jane@example.org",
  init.defaultBranch = "main") # <-- not necessary but kinder than 'master'
```
You will need to do this *once per project*.

You have now built the git, our time machine, for your project. 
But we can't travel to another time yet, because we are in the first version and there is no history from Git's point of view.

#### Make history {-}

Let's make history then.
To do that we need to change something in the document. 
How about the plot in the code? 
Remember, we are currently in <span style="color:orange">inflation.rmd</span>.

<span style="color:green">The plot is ~~ugly~~ very functional. Beautify it a bit. Some suggestions:</span>

```
  theme_minimal() +
  ylab("subjective inflation in %-points") +
  labs(color = "") +
  theme(legend.position = c(.1, .9)) +
```

<span style="color:blue">Plot the the two or five year expectation.</span>

[Hint: Swapping the variable <span style="color:orange">E1y_all</span> in <span style="color:orange">R/prepare_inflation.R</span> should to the trick.]








