# Software Management {-}

```{r results='asis', echo = FALSE}
reprodude4 <- generate_reprodudes(links$reprodudes$four,
                                  "ReproDude",
                                  "Hey, I'm your ReproDude for this chapter. If you have any questions click on me and we can talk!")

cat(reprodude4)

```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>

## What now? {-}

And on to another chapter!
What's next?

Like last time, let's look at our components, which ones are we examining now?

code + data + text + history + <span style="color:orange">software</span> + workflow

Software? Maybe a look at our problem and software solution list will help us again.

Problem list:

1. ~~copy&paste mistakes~~
2. ~~inconsistent versions of code or data~~
3. <span style="color:orange">missing or incompatible software</span>
4. complicated or ambiguous procedure for reproduction

Software solution list:

1. RMarkdown
2. Git
3. <span style="color:orange">Docker</span>
4. Make

So that means we use the Docker to avoid the problem of missing or incompatible software?
This sounds like a program I would have needed for a while. 
Then let's jump right in!

## Docker? {-}

Let me introduce Docker: your software superhero! 
It saves you from compatibility chaos and missing dependencies. 
With Docker, create portable packages called Docker images that effortlessly work on any computer. 
Docker operates on a principle of containerization, which essentially means encapsulating your software application in a bundle with its own operating system, also known as a container. 
This approach provides a unified and consistent environment that is isolated from the rest of your system, ensuring that your software runs the same way, no matter where it is deployed.

Short note from the management, this workshop uses a lot of automation to automate reproducibility, e.g., to configure software, fill templates, interact with Git/GitHub etc.

Among them:

- usethis
- gitcreds
- gh

and a package from Aaron:

- <span style="color:orange">repro</span>

These packages are "training wheels" and not required.

Nevertheless, the use of repro prevents headaches by taking over many steps.
[Besides, it would go beyond the scope of the workshop if we were to do every step ourselves.]

### repro! {-}

```{r results='asis', echo = FALSE}
addinforepro <- generate_additionalinfo(links$addinfos$repro,
                                    "repro",
                                    "I will lead you to a deep dive of the repro package.")

cat(addinforepro)
```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>

<span style="color:orange">repro</span> uses metadata in Rmds to infer (among other things) the software environment required.

<span style="color:green">Trigger this mechanism using: <span style="color:orange">repro::automate()</span></span>

<span style="color:green">Take a look at the newly generated file <span style="color:orange">Dockerfile.</span></span>

<span style="color:green">Remove all, if any, python chunks.</span>

<span style="color:green">Commit changes. (Do not push.)</span>

<span style="color:blue">Add any package of your liking to any Rmd and run <span style="color:orange">repro::automate()</span></span>

<span style="color:blue">Take a look at the file <span style="color:orange">.repro/Dockerfile_base</span> and friends. How would you change the R version used?</span>

Now we will use GitHub action (GHA).
GitHub action is a cloud service that runs software when certain events trigger it.

<span style="color:green">Add a GitHub Action to build the required Docker image with <span style="color:orange">repro::use_gha_docker()</span></span>

<span style="color:green">To trigger the action, commit and push your changes.</span>

<span style="color:green">Browse through the actions: <span style="color:orange">usethis::browse_github_actions()</span></span>

<span style="color:blue">Take a look at <span style="color:orange">.github/workflows/push-container.yml.</span> When is the action triggered?</span>

That's it. 
But what have we actually just done?

We created Dockerfiles using the repro package and then automated the building of Docker images by setting up GitHub Action. 
These Docker images now ensure a reproducible software environment!

## And now? {-}

Congratulations, we are approaching the finish line!

Before we continue, let's take another quick look together at what we have just done.
We have now yet one component more in our toolbox.

<span style="color:orange">code + data + text + history + software</span> + workflow

And with that we solved our third Problem on the list:

1. ~~copy&paste mistakes~~
2. ~~inconsistent versions of code or data~~
3. ~~missing or incompatible software~~
4. complicated or ambiguous procedure for reproduction

And which software did we just use for this:

1. RMarkdown
2. Git
3. <span style="color:orange">Docker</span>
4. Make


### Final Step! {-}

Now please go through what we have just done and all the software we used. 

You are currently at your computer using Posit Cloud which hosts an R environment where you used the repro package and GitHub to generate a Dockerimage to ensure a reproducible software environment.

That ends this section.
Should we pause for a short break or proceed without interruption?

You are now ready for the next chapter. [next chapter](./workflow-orchestration.html).
