# Workflow Orchestration {-}

```{r results='asis', echo = FALSE}
reprodude5 <- generate_reprodudes(links$reprodudes$five,
                                  "ReproDude",
                                  "Hey, I'm your ReproDude for this chapter. If you have any questions click on me and we can talk!")

cat(reprodude5)

```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>

## What now? {-}

We have already reached the last chapter of content!
What is it about?

As usual, let's look at our components.
Which is the last missing piece for fully automating reproducibility?

code + data + text + history + software + <span style="color:orange">workflow</span>

Workflow, I think I heard of that. 
Let's peek again at our problem and software solution lists to be sure.

Problem list:

1. ~~copy&paste mistakes~~
2. ~~inconsistent versions of code or data~~
3. ~~missing or incompatible software~~
4. <span style="color:orange">complicated or ambiguous procedure for reproduction</span>

Software solution list:

1. RMarkdown
2. Git
3. Docker
4. <span style="color:orange">Make</span>

So that means we use Make to avoid the problem of complicated or unclear procedure for reproduction?
Let's jump right in!

## Make? {-}

```{r results='asis', echo = FALSE}
addinfomake <- generate_additionalinfo(links$addinfos$make,
                                    "Make",
                                    "Click on me for the documentation of Make!")

cat(addinfomake)
```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>

To understand what Make is, let's take a step back. 
To do that, let's move on to a topic that I'm really passionate about. 
Food.
And even one step further back, cooking.
What is cooking?

Besides the definition of content, cooking is a sequence of dependencies. 
Let's take a look at my favorite recipe.

>Arrabbiata sauce, or sugo all'arrabbiata in Italian, is a spicy sauce for pasta made from garlic, tomatoes, and dried red chili peppers cooked in olive oil.  
<small>"Arrabbiata sauce" from Wikipedia under [<span style="color:orange">CC BY-SA 3.0</span>](https://en.wikipedia.org/wiki/Wikipedia:Text_of_the_Creative_Commons_Attribution-ShareAlike_3.0_Unported_License)</small>

And what are the steps in this masterpiece of craftsmanship?

>Arrabbiata sauce, or sugo all'arrabbiata in Italian, is a spicy <span style="color:orange">sauce</span> for <span style="color:orange">pasta</span> made from <span style="color:orange">garlic</span>, <span style="color:orange">tomatoes</span>, and dried red <span style="color:orange">chili</span> peppers cooked in olive oil.  
<small>"Arrabbiata sauce" from Wikipedia under [<span style="color:orange">CC BY-SA 3.0</span>](https://en.wikipedia.org/wiki/Wikipedia:Text_of_the_Creative_Commons_Attribution-ShareAlike_3.0_Unported_License), emphasis added</small>

Despite the beauty inherent in this recipe, we also want to formalize it. 
Let's see how this recipe looks in a formalized version:
<!--Python part wieder einfügen? Hat beim rendern zu problemen geführt.-->
```
arrabiata.pdf: arrabiata.Rmd sauce.csv R/pasta.R 
  Rscript -e "rmarkdown::render('arrabiata.Rmd')"
sauce.csv: R/cook.R tomatoes.zip aromatics.yaml
  Rscript -e "source(R/cook.R)"
aromatics.yaml: R/sizzle.R garlic.txt chili.json
  Rscript -e "source(R/sizzle.R)"
```
Let's break it down for our understanding. <span style="color:orange">arrabiata.pdf</span> is our sauce that we want to have.
This sauce is created based on the files <span style="color:orange">arrabiata.Rmd</span>, our recipe, using <span style="color:orange">sauce.csv</span> and <span style="color:orange">/pasta.R</span>.

<span style="color:orange">sauce.csv</span> is created with <span style="color:orange">R/cook.R</span> with the raw materials <span style="color:orange">tomatoes.zip</span> and <span style="color:orange">aromatics.yaml</span>.

<span style="color:orange">aromatics.yaml</span> in turn is created by <span style="color:orange">R/sizzle.R</span> with the raw materials <span style="color:orange">garlic.txt</span> and <span style="color:orange">chili.json</span>.

If you have trouble understanding the recipe, don't worry, we're all just virtual people. 
Maybe a conversation with ReproDude will help you?

After looking at the arrabbiata sauce, here is another example of a culinary masterpiece.

<span style="color:brown">Brownies.</span>

Just kidding, let's get out of here or I'll need a lunch break.

Instead, let's point out the key features of this kind of recipe by Make:

- Missing ingredients will be generated,  
  <small>*e.g., if the cleaned data is missing, the raw data is first cleaned.*</small>

- Newer ingredients trigger updates,  
  <small>*e.g., new data leads to the recreation of the whole manuscript.*</small>

- Always the same "button" that triggers reproduction,  
  <small>*e.g., regardless of programming language, file format, and intermediate steps.*</small>

And the great thing is that <span style="color:orange">repro::automate()</span> automatically generates recipes for Rmds, only deeper nested dependencies must be added manually.

### Hands on! {-}

But now we have had enough thinking, let's go back to the code!

<span style="color:green">Go to the terminal (<span style="color:orange">Alt + Shift + M</span>) and type <span style="color:orange">make inflation.pdf</span></span>

[Hint: If you did not change `output: html_document` to `output: pdf_document` in `inflation.Rmd` you need to use `.html` instead of `.pdf`.]

<span style="color:green">Delete <span style="color:orange">inflation.pdf.</span></span>

<span style="color:green">Add <span style="color:orange">inflation.pdf</span> to the target <span style="color:orange">all </span> (e.g.,: `all: inflation.pdf`) in the <span style="color:orange">Makefile</span>.</span>

<span style="color:green">Go to the terminal (<span style="color:orange">Alt + Shift + M</span>) and type <span style="color:orange">make</span></span>

<span style="color:blue">Run: <span style="color:orange">make -B --dry-run</span></span>

[Hint: <span style="color:orange">-B</span> means rebuild everything. <span style="color:orange">--dry-run</span> means do not actually run the commands.</span>]

And now that we've created the recipe, let's take it one step further and *Make* it in the cloud.

<span style="color:green">Run <span style="color:orange">repro::use_make_publish()</span></span>

<span style="color:green">Paste the following into the <span style="color:orange">Makefile:</span></span>

```
publish/: inflation.pdf
include .repro/Makefile_publish
```

<span style="color:green">Run <span style="color:orange">repro::use_gha_publish()</span></span>

<span style="color:green">Commit and push.</span>

<span style="color:blue">Inspect <span style="color:orange">.repro/Makefile_publish.</span></span>

Ready yet?  
All right, what did we just do?

We created and send a Makefile to the cloud using Make and the repro package.
This makefile will ensure that we can track how our sauce is created!

## And now? {-}

Congratulations, we are more or less near the finish line!

Before we finish, let's take one more quick look together at what we just did.
We now have all the components from our toolbox together.

<span style="color:orange">code + data + text + history + software + workflow</span>

And with that, we solved our last problem on the list:

1. ~~copy&paste mistakes~~
2. ~~inconsistent versions of code or data~~
3. ~~missing or incompatible software~~
4. ~~complicated or ambiguous procedure for reproduction~~

And which software did we use?:

1. RMarkdown
2. Git
3. Docker
4. <span style="color:orange">Make</span>

### Almost the Final Final Step! {-}

Now please go through all the things we just did and all the software we used.

You are currently at your computer using Posit Cloud, which hosts an R environment where you used Make and the repro package to generate a Makefile which automates the reproducibility of build processes.

You have now reached the advanced status of reproducibility; there is only one last step to show the world what we have learned here.

<span style="color:orange">Publish</span>

With this step we will now publish the document automatically, for this we will use GitHub again.

<span style="color:green">Go back to GitHub.</span>

<span style="color:green">Go to Settings → Pages and change <span style="color:orange">none</span> to <span style="color:orange">gh-pages.</span></span>

<span style="color:green">Go to actions and wait for the new action to finish.</span>

<span style="color:green">Inspect the published PDF online (<span style="color:orange">change username</span>):</span>

<span style="color:orange">yourusername.github.io/project/inflation.pdf</span>

<span style="color:blue">Change something, e.g., make the plot ugly again, then commit and push. Takes ~5min or so.</span>

The great thing about this automation is that it now automatically builds and publishes your document every time you push a new version to GitHub.

And with that, we have concluded the workshop in terms of content!
In the following chapter, we'll just go through some suggestions on how you can continue your Reproductions journey.

You are now ready for the last chapter. [next chapter](./before-you-go.html).
