# Before you go {-}

Welcome to the end of our journey!
Now that we have everything behind us, let's take another look at how the individual components work together.

Let's look at everything together again.

```{r, echo=FALSE, out.width='100%'}
knitr::include_graphics("https://raw.githubusercontent.com/aaronpeikert/repro-tutorial/main/images/nutshell.svg")
```

And does it make more sense to you now?
If not, don't worry; practice makes perfect.
Now that we have gathered a lot of knowledge, the journey together is over, but hopefully, your journey has just begun.
To help get you started, here are a few resources.

## Ressources {-}

### Starter {-}

First, we started with RMarkdown.
This was the part where we familiarized ourselves with the files


```{r results='asis', echo = FALSE}
suggestionsrmarkdown <- generate_additionalinfo(links$suggestions$rmarkdown,
                                    "RMarkdown",
                                    "Click on me and I will lead you to R Markdown: The Definitive Guide.")

cat(suggestionsrmarkdown)
```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>


Secondly, we have Git, with which we have recorded our versions and can travel in time.


```{r results='asis', echo = FALSE}
suggestionsgit <- generate_additionalinfo(links$suggestions$git,
                                    "Git",
                                    "Click on me and I will lead you to a specific Git tutorial.")

cat(suggestionsgit)
```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>


Third, we have GitHub, which allows us to store our Git versions online and do a variety of additional things, such as GitHub Actions.
But an even better idea than to use the resources here is to start a small project on GitHub together with a friend.


```{r results='asis', echo = FALSE}
suggestionsgithub <- generate_additionalinfo(links$suggestions$github,
                                    "GitHub",
                                    "Click on me and I will lead you to a Deep Dive tutorial for GitHub.")

cat(suggestionsgithub)
```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>

That's it for the starter tutorials. 

### Advanced {-}

To go deeper, I would recommend you to read the following:

<span style="color:blue">Read: Peikert, A., van Lissa, C. J., & Brandmaier, A. M. (2021). Reproducible Research in R: A Tutorial on How to Do the Same Thing More Than Once. Psych, 3(4), 836–867. https://doi.org/10.3390/psych3040053</span>

And to give you a direct starting point from here, how about this:

<span style="color:blue">Adept the project we created today so that it becomes one of your projects (with your data, your analyses).</span>

### Digging really Deep {-}

As you have probably noticed, we are still missing a deep dive into some of the software we have directly or indirectly used. 
These are a bit more complicated than what we have described so far, so let's just bundle them into this section.
First, Make, which we used to build our recipes.


```{r results='asis', echo = FALSE}
suggestionsmake <- generate_additionalinfo(links$suggestions$make,
                                    "Make",
                                    "Click on me and I will lead you to minimal make: A minimal tutorial on make.")

cat(suggestionsmake)
```
<!-- so that there is no text between the Boxes-->
<div style="clear: both;"></div>


And after you've looked at that:

<span style="color:blue">Simplify a complicated pipeline</span>

Next up is Docker.
Docker is a great program once you get it running.
If you enjoy a bit of a headache:

<span style="color:blue">Docker: get [<span style="color:orange">Docker</span>](`r links$suggestions$docker`) installed.</span>

And if you enjoy severe headaches, welcome to LaTeX.

<span style="color:blue">Try to learn [<span style="color:orange">LaTeX</span>](`r links$suggestions$latex`)</span>

## Hard to say Goodbye {-}

If you're reading this, you're all done with the workshop!
Unless you're just passing through, in which case I hope to see you again later.

Thank you for taking the time to explore the big world of reproducibility with me.

Also, I want to thank my developers, Aaron Peikert and Hannes Diemerling.

And then it only remains for me to say goodbye to you; it was nice to have you here!
